\documentclass[12pt]{article}
\usepackage{geometry}                % See geometry.pdf to learn the layout options. There are lots.
\geometry{letterpaper}                   % ... or a4paper or a5paper or ... 
%\geometry{margin=1in}
%\geometry{ignorefoot}
\usepackage{graphicx}
\usepackage{amssymb}
\usepackage{epstopdf}
\usepackage{amsmath}
\usepackage{mathrsfs}
%\usepackage[numbers,sort&compress]{natbib}
\usepackage{graphicx}
\usepackage{setspace}
\usepackage{url}
\usepackage{subfigure}

\setlength{\paperwidth}{8.5in}
\setlength{\paperheight}{11in}
\setlength{\voffset}{-0.2in}
\setlength{\topmargin}{0in}
\setlength{\headheight}{0in}
\setlength{\headsep}{0in}
\setlength{\footskip}{30pt}
\setlength{\textheight}{9.25in}
\setlength{\hoffset}{0in}
\setlength{\oddsidemargin}{0in}
\setlength{\textwidth}{6.5in}
\setlength{\parindent}{0in}
\setlength{\parskip}{9pt}


\begin{document}
{\centering
Author's Response to Reviewers' Comments \\ Submission COST-D-14-00128 \\ Amelia McNamara

}

\textbf{Author's overall response to reviewers' comments:} Thank you for giving me the opportunity to clean up my submission and resubmit. I hope that the majority of the small errors have been fixed. I have fixed many typos, expanded the captions on all plots, reformatted \verb#knitr# code to be cleaner in \LaTeX\, and clarified some of my arguments. The only comment I have not incorporated into this draft is the suggestion to change some charts to tables. This has been addressed specifically below. I feel much more solid about this submission, and hope it is satisfactory.

\textbf{Reviewers' comments:}

\textbf{The content of the paper is good, but the submission looks like it was rushed. There are a lot of very small errors in the paper that need correcting before it can be reviewed.} 


\textbf{Fig 1. Maps of yearly survey percentages}
          \\  \textbf{No period.} Added.
            \\ \textbf{Explain why this is interesting or useful to know in the caption} All captions have been expanded.

 \textbf{Fig 2. Expand caption, why do we care about the number of levels on the questions} All captions have been expanded.

\textbf{Typos: behaviorsec (page 7)} Removed.

\textbf{Label text on some plots is too small to read} All plot labels have been adjusted for reading clarity.

\textbf{R output needs a little cleaning, runs outside the background box, too many decimals, but it was done in knitr which is a big thing} All knitr output has been sent through \LaTeX \,using functions like \verb#xtable()#, so output should be much cleaner.

  \textbf{Would tables be better than charts for info like fig 7, 9, 13.} These charts have been made slightly larger for easier reading. However, they have not been converted to tables. I believe it is useful to be able to graphically compare communities and groups at the same time, and I believe it is harder to do so using a table. 

  \textbf{Fig 14 should have a square aspect ratio, caption doesn't match x axis label} Aspect ratio has been adjusted, and the entire section text has been clarified so captions should make more sense in the context of the axis labels. 

  \textbf{Section ??? still in document} Fixed.




\end{document} 